30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-14 paper.tex
Made figure span the width of the full page
Added text about the routing attacks

@@

@@

		\begin{figure}[!t]
			\centering
			\includegraphics[width=0.4\textwidth]{graphics/tor.pdf}
			\caption{The components of the Tor network. After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
			\label{fig:tor_layout}
		\end{figure}

@@

	\subsection{Low-Resource Routing attacks}
		Hier wat over routing attacks

>>>>

% setting paragraph indent
\setlength{\parskip}{\baselineskip}

@@

	\begin{figure*}[!t]
		\centering
		\includegraphics[width=0.8\textwidth]{graphics/tor.pdf}
		\caption{The components of the Tor network. After downloading the node list from the Directory Server, the user creates a circuit through a guard node, a relay node and an exit node, and uses it to communicate (anonymously) with the internet.}
		\label{fig:tor_layout}
	\end{figure*}

@@

@@

	\subsection{Low-Resource Routing attacks}
		Another possible attack on the anonimity of tor is the so called \emph{low-resource routing attack} [linkje naar paper]. With this attack, it is possible for an adversary to perform an end-to-end traffic analysis with minimal resourcing, thus comprimising the anonimy Tor provides. The idea of this attack is that a malicious Onion router can lie about it's bandwidth, thus advertising a much higher bandwidth than it actually has. Because of the Tor path selection algorithm that prefers high-bandwidth nodes, the chance that a malicious entry node and exit node are chosen, is high.

		Once a malicious entry node and exit node has been chosen, an analysis of the traffic can be done to link Onion proxies with the webservers he communicates with. Experimental research on a testbed, has shown that with an total of 66 nodes and 6 malicious nodes, is possible to compromise 46\% of the built circuits. On request of the Tor community, this attack hasn't been tested on the live Tor network. There are some extensions and improvements to this attack. It is possible to denial-of-service some of the well-used entry nodes, to force Tor clients to choose a new entry node, possibly a malicious one.

		Bauer et al. proposed several solutions in his paper. The first one is to actually verify the resources of the nodes, for example, measuring the bandwidth and/or uptime of a node. Bandwidth can be checked centralized or decentralize: the disadvantages of a centralized bandwidth check, is that is generates much overhead on the network. With distributed bandwidth verification, Tor routers monitor each other but this is not enough to detect selective malicious nodes. Another solution is to restrict the amount of routers that can be on a single IP-address. The last solution proposed is to change the routing strategy.
